### 2023-04-12 main.tex
ii

\section{Integrability}\label{sectionIntegrabiliy}

@@

@@

that gives back \eqref{one-pts-corr}.  \\ 

>>>>

\section{Exact steady state and arbitrary correlations for the integrable chain}\label{sectionIntegrabiliy}

@@

\section{Steady state for the non-integrable chain}
In Section \ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability. This nice property is lost when we allow an arbitrary maximal occupation $\nu>1$, therefore it is natural to ask if we can still say something about correlations. Again, exploiting duality, steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
\subsection{Steady state correlations and duality}
We consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs. Now, each site can host $\nu\geq 1$ particles, chosen among the $N$ types. The generator reads as
	\mathcal{L}=\mathcal{L}_{1}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{L}
where at the boundaries 
while the bulk generator is 
 \mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{b}^{x}+\delta_{a}^{x+1}-\delta_{b}^{x+1})-f(\bm{n})\right)
This process is dual to $(\bm{\xi}(t))_{t\geq0} $ on the enlarged configuration space
	\widetilde{\Omega}=N_{0}^{N-1}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{L-1}
The dual generator is 
	\widetilde{\mathcal{L}}=\widetilde{\mathcal{L}}_{1}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\widetilde{\mathcal{L}}_{L}
with absorbing boundaries, i.e. 
	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})|}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\widehat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species of types $s_{i}\in\{2,\ldots,N\}$ situated at sites $y_{i}\in\{1,\ldots,L\}$ with $i\in \{1,\ldots,m\}$. This expectation is computed by \eqref{ExptationSS} once the absorption probabilities $a_{i_{s_{a}}}(\widehat{\bm{\xi}})$. The issue is that, usually, these absorption probabilities fulfil some difference equations that are not easy to solve. For example, we report here the solution for the one points correlations. 
we want to determine $a^{x}_{s}(1)=\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries. Therefore, this $a_{s}^{x}(1)$ fulfils the following equations 
that gives back \eqref{one-pts-corr}.

@@

that gives back \eqref{one-pts-corr}.  
